Retrofitting Effect Handlers onto OCaml

### 2021-03-14 retro-concurrency.tex
Revert abstract

\begin{abstract}
Effect handlers have been gathering momentum as a mechanism for non-local
	control flow mechanisms such as generators, async/await, lightweight threads
	and coroutines to be composably expressed. We present a design and evaluate a
	full-fledged efficient implementation of effect handlers for OCaml, an
	industrial-strength multi-paradigm programming language. Our implementation
	strives to maintain the backwards compatibility and performance profile of
	existing OCaml code. Retrofitting effect handlers onto OCaml is challenging
	since OCaml does not currently have any non-local control flow mechanisms
	other than exceptions. Our implementation of effect handlers for OCaml: {\em
	(i)} imposes negligible overhead on code that does not use effect handlers;
	{\em (ii)} remains compatible with program analysis tools that inspect the
	stack; and {\em (iii)} is efficient for new code that makes use of effect
	handlers.
\end{abstract}

>>>>

\begin{abstract}
Effect handlers have been gathering momentum as a mechanism for modular
	programming with user-defined effects. Effect handlers allow for non-local
	control flow mechanisms such as generators, async/await, lightweight threads
	and coroutines to be composably expressed.  We present a design and evaluate a
	full-fledged efficient implementation of effect handlers for OCaml, an
	industrial-strength multi-paradigm programming language. Our implementation
	strives to maintain the backwards compatibility and performance profile of
	existing OCaml code. Retrofitting effect handlers onto OCaml is challenging
	since OCaml does not currently have any non-local control flow mechanisms
	other than exceptions. Our implementation of effect handlers for OCaml: {\em
	(i)} imposes negligible overhead on code that does not use effect handlers;
	{\em (ii)} remains compatible with program analysis tools that inspect the
	stack; and {\em (iii)} is efficient for new code that makes use of effect
	handlers.
\end{abstract}
